\documentclass[a4paper]{report}
\usepackage[a4paper, margin=1in]{geometry}
\usepackage{setspace}
\usepackage[document]{ragged2e}


% \address{Dr. Devchand Chaudhari\\Department of Computer Science \& Engineering\\Government College of Engineering\\Nagpur - 441108 (M.S.)} %
\date{April 22, 2024}

\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=10000
\hbadness=10000
\pagenumbering{gobble}

\begin{document}

\begin{FlushRight}
April 22, 2024
\end{FlushRight}

{Dr. Devchand Chaudhari\\Department of Computer Science \& Engineering\\Government College of Engineering\\Nagpur - 441108 (M.S.)}\\ \bigskip
{Dear Dr. Devchand J. Chaudhari,}\\
\medskip
\textbf{Subject: Request to Close ARA (AI-powered Research Assistant) Project}\\

\begin{justify}
We are writing to request your approval for the closure of our pre-final year project titled "ARA - AI-powered Research Assistant". Our team has successfully completed the development and implementation of the ARA system as per the approved project synopsis.

\medskip

\noindent We have conducted rigorous testing, including unit testing, integration testing, system testing, and user acceptance testing, to ensure the system's functionality, reliability, and performance. The test results, which are documented in the project report, demonstrate that ARA meets all the specified requirements and acceptance criteria.

\medskip

\noindent Throughout the project's lifecycle, we have adhered to industry best practices and followed a structured software development methodology. The project report provides a comprehensive overview of the system's design, implementation details, test results, and other relevant documentation. The project report is submitted as required.

\medskip

\noindent We kindly request your review and approval for closing this project. Upon your approval, we will proceed with the necessary documentation and archiving processes.

\medskip

\noindent Thank you for your guidance and support throughout this project. We look forward to your feedback and decision regarding the project closure.

\medskip
\noindent Thank you for your consideration and understanding.
\end{justify}
\bigskip


Aditya Deshmukh,\\ 
Devansh Parapalli,\\ 
Kaustubh Warade \& \\
Yashasvi Thool \\ 
\smallskip 
Department of Computer Science \& Engineering\\Government College of Engineering, Nagpur\\
Sector-27, MIHAN Rehabilitation Colony\\
Khapri, Nagpur\\
441108\\


\newpage

{\large \textbf{Approval:}}

\bigskip
\bigskip
\bigskip
\bigskip

\begin{spacing}{1.5}
Dr. Devchand Chaudhari\\
Project Guide\\
Assistant Professor, Computer Science and Engineering\\
Government College of Engineering, Nagpur\\
Sector-27, MIHAN Rehabilitation Colony\\
Khapri, Nagpur\\
441108\\
\end{spacing}


\end{document}